 

### 2023-02-28 paper2.Rmd
Adding rayshader to Madagascar maps

@@

ecological_zones <- read_excel(
  paste(data_climate_path,
        "ecological_zones.xlsx",
        sep = "/")) %>%
  rename(ecological_zone = 'ecological_zone (1 = Eastern rainforest; 2 = High Plateau; 3 = Arid/Desert; 4 = Dry Deciduos Forest)',
         REGION_NAM = region_name)

map_mdg_1 %>% inner_join(ecological_zones, by = "REGION_NAM") %>%
  mutate(ecological_zone = ifelse(ecological_zone == 1, "Eastern lowland forests",
                                  ifelse(ecological_zone == 2, "Highland subhumid forests",
                                         ifelse(ecological_zone == 3, "Desert and xeric shrubland", "Dry deciduous forests")))) %>%
  mutate(ecological_zone = factor(ecological_zone, levels = c("Eastern lowland forests",
                                                              "Highland subhumid forests",
                                                              "Desert and xeric shrubland",
                                                              "Dry deciduous forests"))) %>%

  ggplot(aes(geometry = geometry, fill = ecological_zone)) +
  geom_sf(size = 0.2,
          color = col_grey_med,
          alpha = 0.6) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro"),
        legend.position = "right") +
  scale_fill_manual(values = c(col_eco_rainforest,
                               col_eco_highlands,
                               col_eco_arid,
                               col_eco_drydecid),
                    name = "Ecoregion") +
  theme_void()

@@

map_a <- facilities_all_gps %>%
  ggplot(aes(geometry=geometry)) +
  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = source)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "left") +
  scale_color_manual(values = c(col_centroid,
                                col_exact_all,
                                col_exact_rhino,
                                col_exact_val,
                                col_search),
                     name = "GPS type")

map_b <- facilities_all_gps %>%
  mutate(clinic_type_clean = ifelse(clinic_type_clean == "CSB/FSP", "Primary",
                                    ifelse(clinic_type_clean == "CHD", "District hospital",
                                           "Regional/university hospital"))) %>%
  mutate(clinic_type_clean = factor(clinic_type_clean, levels = c("Primary",
                                                                  "District hospital",
                                                                  "Regional/university hospital"))) %>%
  ggplot(aes(geometry=geometry)) +
  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = clinic_type_clean)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "right") +
  scale_color_manual(values = c(col_CSB,
                                col_CHD,
                                col_CHR),
                     name = "Facility type")

@@

ggdraw() +
  draw_image(
    compass_file, scale = .2, x = .51, y = .02,
    hjust = 1, halign = 1, valign = 0
  )  +
  draw_plot(combined_plot)

ggsave(filename = paste0("figure_1.jpg"),
       plot = last_plot(),
       path = analysis_figures,
       width = 16,
       height = 10)

@@

ggsave(filename = paste0("figure_2.jpg"),
       plot = last_plot(),
       path = analysis_figures,
       width = 6,
       height = 7)

>>>>

```{r rayshader}

crsLONGLAT <- "+proj=longlat +datum=WGS84 +no_defs"
map_mdg_0_un <- map_mdg_0_un %>%
  st_as_sf(crs= crsLONGLAT)

# map_mdg_0 <- map_mdg_0 %>%
#   st_as_sf(crs= crsLONGLAT)

library(rayshader)

z_level = 6

country_elevation <- get_elev_raster(
  locations = map_mdg_0_un,
  z = z_level,
  clip = "locations")

extent_map = extent(country_elevation)

country_elevation = raster_to_matrix(country_elevation)

ground_units <- ifelse(z_level == 5, 4892.0, 
                       ifelse(z_level == 6, 2446.0,
                              "ERROR"))

height_max <- max(country_elevation, na.rm = TRUE)

zscale_selected <- ground_units/40

country_elevation %>%
  sphere_shade(colorintensity=0.25,
               sunangle = 360-90+15,
               texture = 
                 create_texture(lightcolor = "#FEFEFE",
                                shadowcolor = "#C6C6C6",
                                leftcolor = "#EAEAEA",
                                rightcolor = "#EAEAEA",
                                centercolor = "#FDFDFD")

                 # grey70","grey60","grey75","grey80","white")
               # create_texture(col_grey_lightest, col_grey_dark, col_grey_med ,col_grey_light,"white")
               # create_texture("#8AD7FE","#051C2D","#1D3EDB","white","white")
               ) %>%
  # add_shadow(ray_shade(country_elevation, zscale = zscale_selected), max_darken=0.95) %>%
  # add_shadow(ambient_shade(country_elevation, zscale = zscale_selected), max_darken=0.95) %>%
  add_water(detect_water(country_elevation), color = "white")  %>%
  save_png(paste0(gpspath_fig, "/elevation_map.png"))

  library(png)

  madagascar_topo_map <- readPNG(source = paste0(gpspath_fig, "/elevation_map.png"))

# Get the spatial extent of the shapefile

  madagascar_bbox <- st_bbox(map_mdg_0_un)

# Get the spatial extent of the PNG image
madagascar_map_bbox <- c(xmin = 0, ymin = 0, xmax = ncol(madagascar_topo_map), ymax = nrow(madagascar_topo_map))

# Calculate the scaling factor for the x-axis
x_scale_factor <- diff(madagascar_bbox[c("xmin", "xmax")]) / diff(madagascar_map_bbox[c("xmin", "xmax")])

# Calculate the scaling factor for the y-axis
y_scale_factor <- diff(madagascar_bbox[c("ymin", "ymax")]) / diff(madagascar_map_bbox[c("ymin", "ymax")])

# Extract minimum and maximum longitude and latitude
min_lon <- as.numeric(bbox["xmin"])
max_lon <-  as.numeric(bbox["xmax"])
min_lat <-  as.numeric(bbox["ymin"])
max_lat <-  as.numeric(bbox["ymax"])

function_add_rayshading <- function(){
   annotation_raster(madagascar_topo_map, 
                    xmin = madagascar_bbox["xmin"], 
                    ymin = madagascar_bbox["ymin"], 
                    xmax = madagascar_bbox["xmax"], # + (1-x_scale_factor * ncol(madagascar_topo_map)), 
                    ymax = madagascar_bbox["ymax"])  # + (1-y_scale_factor * nrow(madagascar_topo_map))) +
  }

@@

map_mdg_1_un %>% rename(REGION_NAM = ADM1_EN) %>% inner_join(ecological_zones, by = "REGION_NAM") %>%
  mutate(ecological_zone = ifelse(ecological_zone == 1, "Eastern lowland forests",
                                  ifelse(ecological_zone == 2, "Highland subhumid forests",
                                         ifelse(ecological_zone == 3, "Desert and xeric shrubland", "Dry deciduous forests")))) %>%
  mutate(ecological_zone = factor(ecological_zone, levels = c("Eastern lowland forests",
                                                              "Highland subhumid forests",
                                                              "Desert and xeric shrubland",
                                                              "Dry deciduous forests"))) %>%
  ggplot(aes(geometry = geometry, fill = ecological_zone)) +
  function_add_rayshading() + 
    geom_sf(size = 0.2,
          color = col_grey_med,
          alpha = 0.4) +
  geom_sf(data = map_mdg_0_un,
          size = 0.2,
          color = col_black,
          fill = NA) +theme(text = element_text(family = "Source Sans Pro"),
        legend.position = "right") +
  scale_fill_manual(values = c(col_eco_rainforest,
                               col_eco_highlands,
                               col_eco_arid,
                               col_eco_drydecid),
                    name = "Ecoregion") +
  theme_void()

@@

map_a <- facilities_all_gps %>%
  ggplot(aes(geometry=geometry)) +
     function_add_rayshading() +

  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = source)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "left") +
  scale_color_manual(values = c(col_centroid,
                                col_exact_all,
                                col_exact_rhino,
                                col_exact_val,
                                col_search),
                     name = "GPS type")

map_b <- facilities_all_gps %>%
  mutate(clinic_type_clean = ifelse(clinic_type_clean == "CSB/FSP", "Primary",
                                    ifelse(clinic_type_clean == "CHD", "District hospital",
                                           "Regional/university hospital"))) %>%
  mutate(clinic_type_clean = factor(clinic_type_clean, levels = c("Primary",
                                                                  "District hospital",
                                                                  "Regional/university hospital"))) %>%
  ggplot(aes(geometry=geometry)) +
    function_add_rayshading() +

  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  geom_sf(alpha = 0.5, aes(color = clinic_type_clean)) +
  theme_void() +
  theme(text = element_text(size = 16, family = "Source Sans Pro"),
        legend.position = "right") +
  scale_color_manual(values = c(col_CSB,
                                col_CHD,
                                col_CHR),
                     name = "Facility type")

@@

ggdraw() +   draw_plot(combined_plot) +
  draw_image(
    compass_file, scale = .2, x = .51, y = .02,
    hjust = 1, halign = 1, valign = 0
  )

ggsave(filename = paste0("figure_1.jpg"),
       plot = last_plot(),
       path = analysis_figures,
       width = 16,
       height = 10,
       bg = "white")

@@

ggsave(filename = paste0("figure_2.jpg"),
       plot = last_plot(),
       path = analysis_figures,
       width = 6,
       height = 7,
       bg = "white")
